Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-22 sections/tensors.tex
some fixes

\subsection{The 8 Key Level Structures}
    The main benefits of specializing to structure come from the following properties of the data:
    \begin{enumerate}
        \item[Sparsity] Sparse data is data that is mostly zero, or some other
        fill value. When we specialize on this data, we can use annihilation ($x
        * 0 = 0$), identity ($x * 1 = 1$), and other constant propagation
        * properties ($ifelse(false, x, y) = y$) to simplify the computation and avoid
        redundant work.

        \item[Blocks] Blocked data is a subset of sparse data where the nonzeros
        are clustered and occur adjacent to one another. This provides us with
        two opportunities: We can avoid storing the locations of the nonzeros
        individually, and we can use a much more efficient randomly accessible
        iterators within the block. \cite{im_optimizing_2001, vuduc_performance_2002, ahrens_looplets_2023}.

        \item[Runs] Runs of repeated values may occur in dense or sparse code,
        cutting down on storage and allowing us to use integration rules such as 
        \mintinline{julia}{for i = 1:n; s += x; end} $\rightarrow$
        \mintinline{julia}{s += n * x} or code motion to lift operations out of loops.

        \item[Singletons] When we have only one non-fill region in sparse data,
        we can use this fact to avoid a loop and instead just compile code for
        only the single region \cite{ahrens_looplets_2023, ghorbani2023compiling}.
    \end{enumerate}

>>>>

\subsection{The 8 Key Level Structures}
    The main benefits of specializing to structure come from the following properties of the data:
    \begin{enumerate}
        \item[Sparsity] Sparse data is data that is mostly zero, or some other
        fill value. When we specialize on this data, we can use annihilation ($x
        * 0 = 0$), identity ($x * 1 = 1$), or other constant propagation
        properties ($ifelse(false, x, y) = y$) to simplify the computation and avoid
        redundant work.

        \item[Blocks] Blocked data is a subset of sparse data where the nonzeros
        are clustered and occur adjacent to one another. This provides us with
        two opportunities: We can avoid storing the locations of the nonzeros
        individually, and we can use more efficient randomly accessible
        iterators within the block. \cite{im_optimizing_2001, vuduc_performance_2002, ahrens_looplets_2023}.

        \item[Runs] Runs of repeated values may occur in dense or sparse code,
        cutting down on storage and allowing us to use integration rules such as 
        \mintinline{julia}{for i = 1:n; s += x end} $\rightarrow$
        \mintinline{julia}{s += n * x} or code motion to lift operations out of loops \cite{donenfeld_unified_2022,ahrens_looplets_2023}.

        \item[Singletons] When we have only one non-fill region in sparse data,
        we can avoid a loop entirely and reduce the complexity of iteration \cite{ghorbani2023compiling, ahrens_looplets_2023}.
    \end{enumerate}
